%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Team Lead Data Platform Engineer} % Job title
    {Brenntag} % Organization
    {Amsterdam, Netherlands} % Location
    {Jul. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built Brenntag Data Platform on AWS/Databricks from scratch, owning architecture design and mentoring team members}
        \item {Drive platform architecture evolution through RFCs and engineering community, ensuring transparent collaborative decisions}
        \item {Maintained hands-on engineering across all platform layers (infrastructure, ingestion, transformation, orchestration, egress) alongside leadership responsibilities }
        \item {Consolidated cloud infrastructure and internal tooling, reducing operational costs by ~€600k/year}
        \item {Reduced onboarding of new Analytics teams from days to hours by providing simple interfaces and documentation}
        \item {Partner with product and engineering teams to ensure platform meets business needs in functionality, reliability, and compliance}
        \item {Managed Agile/Scrum team ceremonies including sprint planning, retrospectives, and refinement}
      \end{cvitems}
      \cvtechstack{Python, SQL, AWS, Databricks, dbt, Airflow, Terraform, Kubernetes}
    }

%---------------------------------------------------------
  \cventry
    {Senior Data Engineer} % Job title
    {Delivery Hero SE} % Organization
    {Berlin, Germany} % Location
    {Nov. 2021 - Jul. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Led CDC solution (Debezium) for data warehousing, reducing costs by ~\$14k/month by removing idle RDBMS read replicas and improving data freshness from 4 hours to seconds}
        \item {Built a Python/FastAPI backend service to manage Kafka Connect connectors, enabling self-service CDC onboarding for engineering teams}
        \item {Owned ingestion, maintenance, and availability of raw and cleansed data for 60+ data sources, including RDBMS (AWS RDS), REST APIs, and S3}
        \item {Implemented GCS/BigQuery Cold Storage solution reducing storage costs by ~\$30k/month}
        \item {Contributed to internal data-platform: reduced CSV/JSON imports failure rate by 20\% via schema evolution; improved performance by implementing parallel jobs for large backfills}
        \item {Advocated knowledge sharing, incentivizing team members to present projects across analytics teams}
        \item {Mentored team members, led onboarding process and maintained documentation/guidelines}
      \end{cvitems}
      \cvtechstack{Python, SQL, AWS, GCP, BigQuery, Airflow, Terraform, Kubernetes, Debezium}
    }

%---------------------------------------------------------
  \cventry
    {Founding Member - Data \& Analytics Consulting} % Job title
    {Waage} % Organization
    {São Paulo, Brazil} % Location
    {Apr. 2016 - Nov. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {\textbf{Bloomin Brands Brazil:} Designed and implemented data platform on Azure (Data Factory, SQL Server DW, SSAS Tabular Models); delivered BI reporting for HR, Finance, Taxes, and Operations using Power BI/Excel/SSRS}
        \item {\textbf{Bacio di Latte:} Built company's first data lake on GCP with Dataflow and Airflow pipelines; integrated social media and internal systems; delivered BI solutions with Power BI and Data Studio}
        \item {\textbf{Synapcom:} Contributed to data lake/warehouse implementation on GCP; built streaming pipelines with Apache NiFi, Debezium, Kafka, and PySpark; implemented IaC (Terraform) and CI/CD on Cloud Build}
      \end{cvitems}
      \cvtechstack{Python, SQL, GCP, Azure, BigQuery, PowerBI, Data Factory, Data Studio, Terraform}
    }

%---------------------------------------------------------
  \cventry
    {Senior Data Analyst} % Job title
    {Telefônica Vivo} % Organization
    {São Paulo, Brazil} % Location
    {Nov. 2014 - Nov. 2017} % Date(s)
    {
      \cvtechstack{Python, SQL, PowerBI}
    }

%---------------------------------------------------------
   \cventry
    {Senior Business Intelligence Analyst} % Job title
    {Bloomin Brands Brazil} % Organization
    {São Paulo, Brazil} % Location
    {Mar. 2012 - Oct. 2014} % Date(s)
    {
    \cvtechstack{Python, SQL}
    }

   \cventry
    {Business Intelligence Analyst} % Job title
    {} % Organization
    {} % Location
    {Feb. 2012 - Mar. 2012} % Date(s)
    {
    \cvtechstack{SQL}
    }
    
   \cventry
    {Intern Financial Planning} % Job title
    {} % Organization
    {} % Location
    {Jun. 2011 - Feb. 2012} % Date(s)
    {}
    

%---------------------------------------------------------
\end{cventries}
